---
title: "Geospatial Techniques for Social Scientists in R"
subtitle: "Wrap Up"
author: "Stefan Jünger & Anne-Kathrin Stroppe<br>February 09, 2021"
output:
  xaringan::moon_reader:
    self_contained: true
    seal: true
    css: ["default", "./assets/css/gesis.css"]
    nature:
      highlightStyle: "github"
      highlightLines: true
      countIncrementalSlides: false
---
layout: true

```{r init-chunk, include = FALSE}
# load all packages
source("../../R/load_packages.R")

# load course content table
source("../../R/course_content.R")

opts_chunk$set(echo = TRUE, fig.align = "center", message = FALSE, cache = TRUE)

options(warn = -1)

xaringanExtra::use_xaringan_extra(c("tile_view", "clipboard"))
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = FALSE  #<<
)
```

---

## Course Content

```{r course-content, echo = FALSE}
course_content
```

---

## Introduction

```{r course-content-1, echo = FALSE}
course_content %>%
  kableExtra::row_spec(1, background = "yellow")
```

---

## Introduction

Main Messages
- Geospatial data are relevant in the social sciences
  - already for a long time
- `R` can serve as a full-blown Geographic Information System (GIS)

---

## Vector Data

```{r course-content-2, echo = FALSE}
course_content %>%
  kableExtra::row_spec(2, background = "yellow")
```

---

## Vector Data

Main Messages
-
-
-

---

## Basic Maps

```{r course-content-3, echo = FALSE}
course_content %>%
  kableExtra::row_spec(4, background = "yellow")
```

---

## Basic Maps

Main Messages
-
-
-

---

## Raster Data

```{r course-content-4, echo = FALSE}
course_content %>%
  kableExtra::row_spec(5, background = "yellow")
```

---

## Raster Data

Main Messages
- Data format for efficient and fast analysis of geospatial data
- flexible in their application
- methods of image processing can be used
  - can get rather involved
- however, straightforward extraction of values

---

## Advanced Data Import

```{r course-content-5, echo = FALSE}
course_content %>%
  kableExtra::row_spec(6, background = "yellow")
```

---

## Advanced Data Import

Main Messages
- Geospatial data tend to be large
- Often distrubuted over the internet
- APIs help in downloading these data
- can get pretty involved

---

## Applied Data Wrangling

```{r course-content-6, echo = FALSE}
course_content %>%
  kableExtra::row_spec(7, background = "yellow")
```

---

## Applied Data Wrangling

Main Messages
- Georeferenced survey data require handling sensitive data
- our example of wrangling and linking data (applications may vary)
- spatial joins are the perfect tool to add geospatial information to other georeferenced data

---

## Advanced Maps I

```{r course-content-7, echo = FALSE}
course_content %>%
  kableExtra::row_spec(9, background = "yellow")
```

---

## Advanced Maps I

Main Messages
-
-
-

---

## Advanced Maps II

```{r course-content-8, echo = FALSE}
course_content %>%
  kableExtra::row_spec(10, background = "yellow")
```

---

## Advanced Maps II

Main Messages
- Drawing maps as in Powerpoint...
- it's coded and thus reproducible
- ...and fun?

---

## What's left

Spatial Analysis
- requires knowledge of spatial statistics
- but definitely the next step

Other map types
- cartograms
- hexagon maps
- animated maps
- ...

More data source
- necessarily limited
- geospatial data are interdisciplinary
  - amount of data feels unlimited