---
# title: 'Exercise 1_2_2 Manipulate Vector Data - Solutions'
title: 'Exercise 1_2_2 Manipulate Vector Data'
author: 'Anne Stroppe, Stefan Jünger'
date: 'Geospatial Techniques for Social Scientists in R'
output:
  # unilur::tutorial_html: default
  unilur::tutorial_html_solution: default
---

```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}
# custom boxes
knitr::opts_template$set(
  clues = list(box.title = "Clues",
               box.body = list(fill = "#fff9dc", colour = "black"),
               box.header = list(fill = "#ffec8b", colour = "black"),
               box.icon = "fa-search",
               box.collapse = TRUE)
)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy()
```



```{block, box.title = "1", box.body = list(fill = "white"), box.icon = "fa-star"}
Import the ESRI shapefile of German districts and the district attribute table.
Join the two data frames, transform the CRS to "EPSG:3035" and check your changes. 

```

```{block, opts.label = "clues"}

You need to rename one of the id variables or adjust your join accordingly ("id = district_id").

```


```{r first-exercise, solution = TRUE, eval = FALSE}

# Import data
german_districts <- st_read(dsn = "./data",
                           layer = "GER_DISTRICTS") %>% 
                     rename(., district_id = id) #

attributes_districts <-  read.csv("./data/attributes_districts.csv", 
                                  header = T, fill = T, sep = ",") 


# Join data and transform
german_districts_enhanced <- 
  german_districts %>% 
  left_join(., attributes_districts, by = "district_id") %>% 
  st_transform(., crs = 3035)

# Check
st_crs(german_districts_enhanced)
head(german_districts_enhanced, 2)

```

```{block, box.title = "2", box.body = list(fill = "white"), box.icon = "fa-star"}

We want a first descriptive visual of the distribution of Covid-19 cases in Cologne and the surrounding districts. 
Calculate the number of Covid-19 cases in the last 7 days (*cases_7days*) by population (population) and multiply with 100,000 (in Germany usually called "7 Tages Inzidenzzahl). 

Select Cologne (district_id == 5315), find the surrounding districts and plot the Covid Rate in Cologne and the surrounding districts.

```

```{block, opts.label = "clues"}

You can use the dplyr function `bind_rows` to combine the two spatial objects "Cologne" and "Cologne Surroundings".

```

``````{r second-exercise, solution = TRUE, eval = FALSE}

# calculate Covid-19 rate
german_districts_enhanced <-
  german_districts_enhanced %>% 
  mutate(covid7d_rate = (cases_7days / population) * 100000)

# filter Cologne
cologne <-
  german_districts_enhanced %>% 
  filter(. , district_id == 5315)

# filter surrounding districts, append with Cologne data and select the Covid column
cologne_sur <-
  german_districts_enhanced %>%
  filter(lengths(st_touches(., cologne)) > 0) %>% 
  bind_rows(., cologne) %>%   
  select(. , covid7d_rate)

# plot  
plot(cologne_sur)


```



```{block, box.title = "3", box.body = list(fill = "white"), box.icon = "fa-star"}

Save your data set of Cologne and its surrounding districts as a ESRI Shapefile. 

```

```{r third-exercise, solution = TRUE, eval = FALSE}

# Export as Shapefile
st_write(cologne_sur, 
         dsn = "./data/own_materials/cologne_covid19_eps3035", 
         delete_layer = TRUE) #optional

  
```
