---
#title: 'Exercise 1_2_1 Import and Explore Vector Data - Solutions'
title: 'Exercise 1_2_1 Import and Explore Vector Data'
author: 'Anne Stroppe, Stefan Jünger'
date: 'Geospatial Techniques for Social Scientists in R'
output:
  unilur::tutorial_html: default
  # unilur::tutorial_html_solution: default
---

```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}
# custom boxes
knitr::opts_template$set(
  clues = list(box.title = "Clues",
               box.body = list(fill = "#fff9dc", colour = "black"),
               box.header = list(fill = "#ffec8b", colour = "black"),
               box.icon = "fa-search",
               box.collapse = TRUE)
)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy()
```

Let's get started with some hands-on exercises and exploring some data!
This exercise focuses on how to import different vector data geometries from different data sources and get used to simple feature data tables.

In the folder "data" you can find the data files we prepped for all the exercises which rely on preexisting data sets. 
However, if you like to play around with your own data, feel free to do so!
. 

```{block, box.title = "1", box.body = list(fill = "white"), box.icon = "fa-star"}
Load the administrative borders of Germany. Therefore, import the shapefile "GER_COUNTRY" from the respective folder and assign the data to an object named "germany". 

```

```{block, opts.label = "clues"}
Don't forget to load the packages "sf" and set your working directory before starting this exercise.
```

```{r first.exercise, solution = TRUE, eval = FALSE}

library(sf)

germany <- st_read(dsn = "./data",
                           layer = "GER_COUNTRY") 

```

The output in the console of the *RStudio* interface gives you already some information on the data you just loaded. You also see that the object "germany" appeared on your environment.
Though, we will explore the data set a little bit closer.

```{block, box.title = "2", box.body = list(fill = "white"), box.icon = "fa-star"}

Explore the data, plot the data and answer the following questions:

  - What is the geometry type? 
  - What is the id of the coordinate refernce system ?
  - Which kind of class is the object?
  - What is the name of the column containing the information on geometries?
  - Which attributes are assigned to the geometries?
  - What was the population size in Germany in 2017?

```

```{r second-exercise, solution = TRUE, eval = FALSE}

st_geometry(germany) # Multpolygon: Set of several Polygons. Each row is a polygon.
class(germany) # "sf" and "data.frame"
attr(germany, "sf_column") # geometry
st_crs(germany) # ETRS89, ID = EPSG:4258
head(germany) # Name, Area Type, Area Size, Population Size
table(germany$population) # 82,792,351 inhabitants


```
