---
# title: 'Exercise 1_1_1: Import Vector Data'
title: 'Exercise 1_1_1: Import Vector Data - Solution'
author: 'Stefan Jünger & Anne Kathrin Stroppe'
date: 'Geospatial Techniques for Social Scientists in R'
output:
   # unilur::tutorial_html: default
    unilur::tutorial_html_solution: default
---

```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}
# custom boxes
knitr::opts_template$set(
  clues = list(box.title = "Clues",
               box.body = list(fill = "#fff9dc", colour = "black"),
               box.header = list(fill = "#ffec8b", colour = "black"),
               box.icon = "fa-search",
               box.collapse = TRUE)
)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy()
```

Let's get started with some hands-on exercises and exploring some data!
This exercise focuses on importing different vector data geometries from various data sources and getting used to simple feature data tables.

In the folder `data`, you can find the data files we prepped for all the exercises which rely on preexisting data sets. 
However, if you like to play around with your own data, feel free to do so!
. 

```{block, box.title = "1", box.body = list(fill = "white"), box.icon = "fa-star"}
Load the administrative borders of Germany. Therefore, import the shapefile "GER_COUNTRY" from the respective folder and assign it to an object named "germany". 

Plot the newly created object.

```

```{block, opts.label = "clues"}
Don't forget to load the packages "sf" and set your working directory before starting this exercise.
```

```{r first.exercise, solution = TRUE}

library(sf)

germany <- sf::st_read(dsn = "../data",
                  layer = "GER_COUNTRY") 

plot(germany)

```

The output in the console of the *RStudio* interface gives you already some information on the data you just loaded. You also see that the object "germany" appeared in your environment.
Though, we will explore the data set a little bit closer.

```{block, box.title = "2", box.body = list(fill = "white"), box.icon = "fa-star"}

Explore the data and answer the following questions:

  - What is the geometry type? 
  - What is the id of the coordinate reference system?
  - Which kind of class is the object?
  - What is the name of the column containing the information on geometries?
  - Which attributes are assigned to the geometries?
  - What was the population size in Germany in 2017?

```

```{r second-exercise, solution = TRUE}

sf::st_geometry(germany) # Multipolygon: Set of several Polygons. Each row is a polygon.
class(germany) # "sf" and "data.frame"
attr(germany, "sf_column") # geometry
sf::st_crs(germany) # ETRS89, ID = EPSG:4258
head(germany) # Name, Area Type, Area Size, Population Size
table(germany$population) # 82,792,351 inhabitants


```

```{block, box.title = "3", box.body = list(fill = "white"), box.icon = "fa-star"}

Do you have an idea why there are 11 observations instead of only one, even though we expected a shapefile with a polygon of just Germany?
Create a new object which contains only one observation holding information on area size and population of Germany.

```

```{r third-exercise, solution = TRUE}

# It seems like the shapefile contains not only the land area of Germany but also coastal areas and lakes.

# filter 
germany_new <-
  germany %>% 
  dplyr::filter(. , area_size != 0)

germany_new

```